---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# admiralverse

<!-- badges: start -->
<!-- badges: end -->

<div style="background-color: #ffcccc; padding: 10px; border: 1px solid 
#ff0000; border-radius: 5px;">

**WARNING:** This admiralverse is a toy example. For real code see the [pharmaverse.org](https://pharmaverse.org/).

</div>

----

The goal of admiralverse is to model the main use case of the
[dverse](https://maurolepore.github.io/dverse/) package.

Explore the [source code](https://github.com/maurolepore/admiralverse) of this
package to learn how to create a minimal meta-package for any collection of R
packages (i.e. a universe), and a website that allows users to search vignettes,
datasets, and functions across the entire universe.

## Installation

You can install the development version of admiralverse from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("maurolepore/admiralverse")
```

## Example

```{r example}
library(admiralverse)
```
