---
title: "Creating a better universe"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)

library(link)
link::auto()
```

**How to create a global search across an entire collection of R packages: A use case for the toy 'admiralverse'**

----

This article shows how to create a global search for any collection of R
packages, i.e. a universe. Your universe may be on CRAN, large, and popular like
the [tidyverse](https://tidyverse.org/) or
[pharmaverse](https://pharmaverse.org/). But it may also be not on CRAN, small,
company-specific or personal.

The example here uses the 'admiralverse' -- a toy universe defined as every
package on CRAN today (2024-12-07), with a website, and a name starting with
'admiral'.

You need:

* the {dverse} package, 
* each package in the toy 'admiralverse',
* {dplyr} to manipulate the output of {dverse}, and 
* {DT} to create a searchable table.

```{r packages}
library(dverse)
library(admiral)
library(admiraldev)
library(admiralonco)
library(admiralophtha)
library(admiralpeds)
library(admiralvaccine)
library(dplyr)
library(DT)
```

<details><summary>Versions</summary>

```{r versions}
packageVersion("dverse")
packageVersion("admiral")
packageVersion("admiraldev")
packageVersion("admiralonco")
packageVersion("admiralophtha")
packageVersion("admiralpeds")
packageVersion("admiralvaccine")
packageVersion("dplyr")
packageVersion("DT")
```

</details>

dverse::document_universe() takes the names of the packages in the
'admiralverse', and a template pointing to each help file (topic) in each
package.

```{r docs}
admiralverse <- c(
  "admiral",
  "admiraldev",
  "admiralonco",
  "admiralophtha",
  "admiralpeds",
  "admiralvaccine"
)
# For example: https://pharmaverse.github.io/admiral/reference/queries.html
template <- "https://pharmaverse.github.io/{package}/reference/{topic}.html"

docs <- dverse::document_universe(admiralverse, template)
docs
```

You may need to exclude some topics, such as reexported objects from other
packages. Because topics outside your universe yield broken links, you can
exclude them with dverse::is_online().

```{r online}
docs |> filter(!dverse::is_online(topic))

online <- docs |> filter(dverse::is_online(topic))
```

Consider the different kinds of documentation in your universe.

```{r kinds}
online |> count(type, keyword)
```

Here it makes sense to separate vignettes, datasets, and public functions.

### Vignettes

```{r vignettes}
vignettes <- online |> filter(type == "vignette")

vignettes |>
  distinct(topic, title, package) |>
  datatable(escape = FALSE)
```

### Datasets

You may also want to search for datasets.

```{r datasets}
datasets <- online |> filter(keyword == "datasets")

datasets |>
  distinct(topic, title, package) |>
  datatable(escape = FALSE)
```

### Functions

```{r public}
internal <- online |> filter(keyword == "internal")

public <- online |>
  anti_join(vignettes) |>
  anti_join(datasets) |>
  anti_join(internal)

public |>
  distinct(topic, title, package) |>
  datatable(escape = FALSE)
```

### Learn More

To learn more see the toy 'admiralverse'
[meta-package](https://maurolepore.github.io/admiralverse) -- which models the
main use case of {dverse}.

You may also enjoy these videos:

* Creating a meta-package for the toy 'admiralverse' ([5'](https://youtu.be/ezVpsadSF7A)).
* Creating a website for the toy 'admiralverse' ([9'](https://youtu.be/VhmnADBDXv0)).

Was this useful? Do you want to [report bugs, propose changes or request
features](https://github.com/maurolepore/dverse/issues).

[Let's connect](https://www.linkedin.com/in/mauro-lepore/).
